No Correlations were Found between the efforts made by the Staff of Toronto's Central Intake Line and Toronto's Homeless Death Counts

### 2024-01-22 outputs/paper/paper.qmd
finished section 2.3

Talk way more about it.

## Using Data from Different Datasets {#sec-data-diff-datasets}

>>>>

## Using Data from Different Datasets {#sec-data-diff-datasets}
During the data cleaning process, code chunks are written to ensure that both the Central Intake Call Wrap-Up Codes Dataset [@Central_Intake_Call] and the Deaths of People Experiencing Homelessness Dataset [@Homeless_Death_Count] are filtered to include only data between November 1st, 2020 to June 30st, 2023.

The decision to only include this time period is reached by taking the common time period between the two datasets. In the latest refresh, the Central Intake Call Wrap-Up Codes Dataset [@Central_Intake_Call] begins on November 3rd, 2020 and end on December 31st, 2023; whereas the Deaths of People Experiencing Homelessness Dataset [@Homeless_Death_Count] begins on January of 2017 and ends on June 2023.

The ultimate purpose of taking the common time period is to ensure that we can plot variables of interest in the two datasets onto the same graph.
